3.3 OLS: OLS: Model Specification Strategies - R Practice

### 2019-10-29 content/r/15-practice.Rmd
Tweaks to R practice 15

- [<i class="fas fa-table"></i> `congress-trump-score.csv`](/data/speeding-tickets.csv)
This data comes from a paper by Makowsky and Strattman (2009) that we will examine later. Even though state law sets a formula for tickets based on how fast a person was driving, police officers in practice often deviate from that formula. This dataset includes information on all traffic stops. An amount for the fine is given only for observations in which the police officer decided to assess a fine. There are a number of variables in this dataset, but the one's we'll look at are:

@@

### Part C
Use the "true" model (Question 7), the "omitted" regression (Question 4), and our "auxiliary" regression (Question 11) to identify each of the following parameters that describe our biased estimate of the marginal effect of `Age` on `Amount`:^[See the notation from class 3.2.]
$$\alpha_1=\beta_1+\beta_2\delta1$$

>>>>

- [<i class="fas fa-table"></i> `speeding_tickets.csv`](/data/speeding_tickets.csv)
This data comes from a paper by Makowsky and Strattman (2009) that we will examine later. Even though state law sets a formula for tickets based on how fast a person was driving, police officers in practice often deviate from that formula. This dataset includes information on all traffic stops. An amount for the fine is given only for observations in which the police officer decided to assess a fine. There are a number of variables in this dataset, but the one's we'll look at are:

@@

### Part C
Use the "true" model (Question 7), the "omitted" regression (Question 4), and our "auxiliary" regression (Question 11) to identify each of the following parameters that describe our biased estimate of the marginal effect of `Age` on `Amount`:^[See the notation from class 3.2.]
$$\alpha_1=\beta_1+\beta_2\delta_1$$

### 2019-10-29 static/r/15-r-practice-rmd.Rmd
Tweaks to R practice 15

- [<i class="fas fa-table"></i> `congress-trump-score.csv`](/data/speeding-tickets.csv)
This data comes from a paper by Makowsky and Strattman (2009) that we will examine later. Even though state law sets a formula for tickets based on how fast a person was driving, police officers in practice often deviate from that formula. This dataset includes information on all traffic stops. An amount for the fine is given only for observations in which the police officer decided to assess a fine. There are a number of variables in this dataset, but the one's we'll look at are:

@@

Use the "true" model (Question 7), the "omitted" regression (Question 4), and our "auxiliary" regression (Question 11) to identify each of the following parameters that describe our biased estimate of the marginal effect of `Age` on `Amount`:^[See the notation from class 3.2.]
$$\alpha_1=\beta_1+\beta_2\delta1$$

>>>>

- [<i class="fas fa-table"></i> `speeding_tickets.csv`](/data/speeding-tickets.csv)
This data comes from a paper by Makowsky and Strattman (2009) that we will examine later. Even though state law sets a formula for tickets based on how fast a person was driving, police officers in practice often deviate from that formula. This dataset includes information on all traffic stops. An amount for the fine is given only for observations in which the police officer decided to assess a fine. There are a number of variables in this dataset, but the one's we'll look at are:

@@

Use the "true" model (Question 7), the "omitted" regression (Question 4), and our "auxiliary" regression (Question 11) to identify each of the following parameters that describe our biased estimate of the marginal effect of `Age` on `Amount`:^[See the notation from class 3.2.]
$$\alpha_1=\beta_1+\beta_2\delta_1$$
